### 2019-05-28 dantzig_selector/report/4_simulation.tex
Proof: Expectation of
Create ConTeXt slides

\Result
{Definition}
{
For \m {\V{x} \in \MB {V}_{\MB {C}} \SB {M}}, we say that \m {\MC {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
\Disp {
\NC \MC {R} \SB {\V{x}}
\in \NC \MB {V}_{\MB {R}} \SB {2M} \NR
\NC \MC {R} \SB {\V{x}} \DB {m}
= \NC \startcases
\NC \MF {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' 
= \NC  0, 1, 2, \dots, M-1 \NR
}
The bijectivity is obvious, and we define \m {\MC {R} ^{-1}} so that
\Disp {
\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V{x}}}
=\NC \V{x} \NR[+]
}
}

@@

\Result
{Definition}
{
For \m {\M{A} \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say that \m {\MC {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
\Disp {
\NC \MC {R} \SB {\M{A}}
\in \NC \MB {M}_{\MB {R}} \SB {2M_1, 2M_2} \NR
\NC \MC {R} \SB {\M{A}} \DB {m_1,m_2} =
\NC \startcases
\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1 
= \NC 0, 1, 2, \dots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \dots, M_2 -1 \NR
}
Notice that Here not all matrices in \m {\MB {M}_{\MB {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
}

@@

\Disp {
\NC {\V {u}}_{n_h}
\in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
\NC {\V {u}}_{n_h} \DB {n_h'}
= \NC
\startcases
1, \quad \MC n_h' =n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h} \in \NC \MB {M}_{\MB {R}} \SB {2N_h, 2N_h} \NR
\NC {\T {\M {U}}}_{n_h} \DB {n_h', n_h''}
= \NC
\startcases
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}
Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V{m}}

\Disp{
\NC \V {m} \NC \in \MB {V}_{\MB {R}} \SB {N_h} \NR
\NC \V{m} \DB{n_h}
= \NC \Nm{\V{g} \DB{n_h}} \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}

to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now take the form
\Disp {
\NC \Hat {\T {\V {g}}}
= \NC \startcases
\NC \Min {\T {\V {g}}', \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \Rm {subject} \; \Rm {to} \quad
\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
\leq \g \NR
\stopcases \NR[+]
\NC n_h 
= \NC 0, 1, 2, \dots, N_h-1 \NR
}

@@

\Disp{
\NC \M{A}_i
= \NC \startTheMatrix
\NC \T {\M {U}}_{i}, \NC \M{0} \NR
\stopTheMatrix \NR[+]
\NC \V{b}_i
= \NC \V{0} \NR[+]
\NC \V{c}_i
= \NC \startTheMatrix
\NC \V{0} \NR
\NC \V {u}_{i} \NR
\stopTheMatrix \NR[+]
\NC d_i
= \NC 0 \NR[+]
\NC i 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}

@@

\Disp{
\NC \M{A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
\stopTheMatrix \NR[+]
\NC \V{b}_i
=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
\NC \V{c}_i
= \NC \V{0} \NR[+]
\NC d_i
= \NC \g \NR[+]
\NC i 
= \NC N_h, N_h +1, N_h +2, \dots, 2N_h -1 \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_y}}, \m{\g > 0}.
\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
\item Calculate
\Disp{
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}' \in \MB {V}_{\MB {C}} \SB {N_h}}
\MC \IP {\V {t}, \V {x}'} \NR[+]
\NC \Rm {subject} \; \Rm {to}
\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
\NC \MC i 
=0, 1, 2, \dots, 2N_h -1 \NR
\stopcases \NR[+]
}
\item Extract
\Disp{
\NC \Hat{\T{\V{g}}}
\LA \NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
}
\item Convert 
\Disp{
\NC \Hat{\V{g}}
\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

>>>>

\Result
{Definition}
{
For \m {\V{x} \in \MB {V}_{\MB {C}} \SB {M}}, we say that \m {\MC {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
\Disp {
\NC \MC {R} \SB {\V{x}}
\in \NC \MB {V}_{\MB {R}} \SB {2M} \NR
\NC \MC {R} \SB {\V{x}} \DB {m}
= \NC \startcases
\NC \MF {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
The bijectivity is obvious, and we define \m {\MC {R} ^{-1}} so that
\Disp {
\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V{x}}}
=\NC \V{x} \NR[+]
}
}

@@

\Result
{Definition}
{
For \m {\M{A} \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say that \m {\MC {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
\Disp {
\NC \MC {R} \SB {\M{A}}
\in \NC \MB {M}_{\MB {R}} \SB {2M_1, 2M_2} \NR
\NC \MC {R} \SB {\M{A}} \DB {m_1,m_2} =
\NC \startcases
\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}
Notice that Here not all matrices in \m {\MB {M}_{\MB {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
}

@@

\Disp {
\NC {\V {u}}_{n_h}
\in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
\NC {\V {u}}_{n_h} \DB {n_h'}
= \NC
\startcases
1, \Q \MC n_h' =n_h \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h} \in \NC \MB {M}_{\MB {R}} \SB {2N_h, 2N_h} \NR
\NC {\T {\M {U}}}_{n_h} \DB {n_h', n_h''}
= \NC
\startcases
1, \Q \MC n_h' =2n_h,\; n_h'' =2n_h \NR
1, \Q \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \ldots, N_h -1 \NR
}
Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V{m}}

\Disp{
\NC \V {m} \in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
\NC \V{m} \DB{n_h}
= \NC \Nm{\V{g} \DB{n_h}} \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \ldots, N_h -1 \NR
}
to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now takes the form
\Disp {
\NC \Hat {\T {\V {g}}}
= \NC \startcases
\NC \Min {\T {\V {g}}', \V {m}} \Q
\MC \IP { \V {1}, \V {m} } \NR
\NC \Rm {subject} \; \Rm {to} \Q
\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
\leq \g \NR
\stopcases \NR[+]
\NC n_h 
= \NC 0, 1, 2, \ldots, N_h-1 \NR
}

@@

\Disp{
\NC \M{A}_i
= \NC \startTheMatrix
\NC \T {\M {U}}_{i}, \NC \M{0} \NR
\stopTheMatrix \NR[+]
\NC \V{b}_i
= \NC \V{0} \NR[+]
\NC \V{c}_i
= \NC \startTheMatrix
\NC \V{0} \NR
\NC \V {u}_{i} \NR
\stopTheMatrix \NR[+]
\NC d_i
= \NC 0 \NR[+]
\NC i 
= \NC 0, 1, 2, \ldots, N_h -1 \NR
}

@@

\Disp{
\NC \M{A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
\stopTheMatrix \NR[+]
\NC \V{b}_i
=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
\NC \V{c}_i
= \NC \V{0} \NR[+]
\NC d_i
= \NC \g \NR[+]
\NC i 
= \NC N_h, N_h +1, N_h +2, \ldots, 2N_h -1 \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_y}}, \m{\g > 0}.
\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
\item Calculate
\Disp{
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}' \in \MB {V}_{\MB {C}} \SB {N_h}}
\MC \IP {\V {t}, \V {x}'} \NR[+]
\NC \Rm {subject} \; \Rm {to}
\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
\NC \MC i 
=0, 1, 2, \ldots, 2N_h -1 \NR
\stopcases \NR[+]
}
\item Extract
\Disp{
\NC \Hat{\T{\V{g}}}
\LA \NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
}
\item Convert 
\Disp{
\NC \Hat{\V{g}}
\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}
